### 2013-09-30 Publications/2013-ISBI14/04-results.tex
Added future lines as Kieran suggested

>>>>

This work presents an evaluation framework that will be extended
in order to evaluate numerous different susceptibility distortion
configurations, better characterizing the phenomenon. Also, the
framework can be used for studying the impact of other artifacts
as subject's motion or eddy currents-derived distortions.
